Paper Figures and Text

### 2024-03-19 Fish Data Analysis/Paper_Figures.qmd

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_close)

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_far)

heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

>>>>

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_close)

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Type + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_far)

heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ", line = Type)))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(size = 3)+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 2)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))
